Gelation as a condensation frustrated by hydrodynamics and mechanical tension

### 2015-09-17 gel_cond/trunk/paper.tex
Remove old text.

\section{Cluster aggregation} % Subject I: Cluster formation
% Topic sentence
Figure~\ref{fig:methods}a shows the phase diagram of all samples.
First of all, we focus on cluster formation since clusters constitute ``building blocks'' of gels.
% Results of birth
Figure~\ref{fig:fluid_dilute} a shows the compaction dynamics of the clusters with three colloids in the early stage.
The results show that the clusters can hardly accomplish compaction within one Brownian motion time and clusters with four and five colloids show very similar tendency (Supplement).
% Explanation 1) Local energy minimization.
If one assumes that each colloid can move independently by Brownian motion and static short-range attractions are induced between colloids, the clusters with three colloids should reach the compact states within one Brownian motion time.
This explanation contradicts to our results.
% Addressing our question
In other words, some interactions stabilize linear structures, competing with the principle of energy minimization.
% Explanation 2) Electrostatic repulsion.
Although the effect of electrostatic repulsions has been studied, our results are observed after salt screens surface charges and electrostatic repulsions can be negligible in our system.
% Explanation 3) Hydrodynamic interactions.
Thus, the only possible explanation is the effect of hydrodynamic interactions.
Hydrodynamic interactions originate from the incompressivility of the solvent, whose effect between colloids have been demonstrated by both numerical simulations and the experiments of optical tweezers.
For compaction, clusters must squeeze the solvent inside the cluster to the outside.
% Conclusion.
Our results suggest that squeezing process can be the bottleneck of compaction and hydrodynamic interactions enhance linear structures in clusters.

% Results of growth
% topic sentence
To investigate whether clusters can reach compact states in their growing stage, fractal dimension of each time is analysed in Figure~\ref{fig:fluid_dilute}b.
% General explanation about fractal dimension.
In general, compact clusters have df around three, whereas chain-like clusters have df around one.
%Our results of fractal dimensions
Our results show that df increases from 1 in the early stage to 2 in the late stage but df is much lower than three.
% Explanation 1) DLCA
Previously diffusion limited cluster aggregation model has been proposed to explain uncompact structures of clusters, assuming sticky attractions.
But DLCA model predicts that df is always fixed around 1.85, which contradicts to our results.
% Addressing our question
Therefore, other mechanism should decrease df close to 1 from condensation equilibrium.
% Explanation 2) Hydrodynamic interactions
As discussed in the early stage of cluster formation, hydrodynamic interactions can frustrate condensation of clusters.
If clusters form chain-like structures, clusters can both avoid squeezing process and decrease resistance from external flow.
Therefore, structures of df = 1 are hydrodynamically favored though energetically disfavored.
% Conclusion
Our results suggest that hydrodynamic interactions dominate the system in the early stage.
As the cluster aggregation proceeds, each colloid can access to a more compact state, squeezing out the solvent in the cluster, and df gradually increases.

\section{Dilute gels} % Subject II: Dilute gels
% Topic sentence
Next, we focus on the mechanism of gelation in a dilute system.
% Our results
Figure~\ref{fig:general}c-h shows the process of gelation of phi = 7\%.
Clusters grow by connecting with each other and the radius of gyration of the biggest cluster finally becomes comparable to the system size as shown in Figure~\ref{fig:fluid_dilute}c. 
Figure~\ref{fig:fluid_dilute}b shows that fractal dimension of clusters increase from 1 in the early stage to 2 in the late stage as similar with the case of cluster aggregation.
% Addressing our question
One can address a natural question about dilute gels: Why can the system percolate with phi of only 7\%?
% Introduction to effective phi
Number density of colloids has little importance since fractal dimension of the system is much lower than three and it changes during the gelation process.
% Procedure to calculate the effective volume
To calculate the ‘ effective ’ volume fraction of colloid, we replace each cluster with the effective sphere whose radius is equal to the radius gyration of the cluster.
% Results of effective phi
As shown in Figure~\ref{fig:fluid_dilute}, the effective volume fraction increases from 7\% in the early stage to 60\% in the late stage.
% Discuss the mechanism of percolation in a dilute gel
Our results clearly reveal that the system cannot avoid percolation because the effective volume fraction is too high.
The reason for the 10 times increase of the effective phi is that df is much lower than three.
The low df originates from hydrodynamic interactions.
% Conclusion
Therefore, percolation in a dilute system is a consequence of condensation frustrated by hydrodynamic interactions.

\section{Dense gels} % Subject III: Dense gels
% Topic sentence
Gelation in a dense system, on the other hand, behaves different patterns than in a dilute system.
% Results of the entire process of dense gelation
As shown in Figure~\ref{fig:dense}a, the system accomplishes percolation in a few minutes, whereas coarsening process proceeds for several hours.
% Focusing on percolation mechanism
% Results of percolation
When the system percolates at t = 5 min, the averaged number of nearest neighbours is only three and the averaged bond-bond angle is 105 deg.
Thus, the network right after percolated has chain-like structures instead of condensed domains.
% Discussions of percolation
As shown in Figure~\ref{fig:fluid_dilute}a, the aggregated clusters in the early stage have linear structures by the effect of hydrodynamic interactions.
In a dense system, linear clusters are generated simultaneously in a high density.
The clusters connect with each other before they can reach compact states and form chain-like networks within a few Tb.
% Conclusion
Therefore, percolation in a dense system is a consequence of condensation frustrated by hydrodynamic interactions.

% Focusing on coarsening mechanism
The coarsening proceeds for a long term.
% General discussion
So, each colloid can access an energetically favoured structure by thermal fluctuations.
As condensation proceeds, each colloid is captured in a ‘ cage ’ of nearest neighbours and finally arrested in a deep energy potential.
This model is consistent with the previous suggestions based on the glass transition.
% Introduction for elementary process of coarsening
But the elementary process of coarsening has been unknown.
In the early stage at t = 5 min, more than 99\% of all colloids connect with a single network.
When one colloid moves to form a compact domain, the network interconnected with the colloid should cooperatively move.
Therefore, coarsening process is frustrated by mechanical tensions and the mechanism to overcome the frustration for further condensation has great importance in basic research.
% Results of NW cutting
Figure~\ref{fig:dense}b-d shows an elementary process of coarsening, in which networks coarsens by seizing a part of the network.
The single strand is strained between two strong chains.
After stretched straight, the strand is seized and the fragments are integrated into strong chains.
% Conclusion of elementary process of NW coarsening
Therefore, the system can selectively seize weak chains of the network by inducing mechanical tensions and condensation proceeds until the local structures of the network are strong enough.

\section{Conclusion} % Conclusion of this study
% Topic sentence
In this study, we analyse the entire process of colloidal gelation in a single particle level.
% Universality of colloidal gelation
To show the universality of colloidal gelation, Figure~\ref{fig:general} summarizes the processes of all our data of gel samples.
In a dilute system, local condensation proceeds simultaneously as percolation.
In contrast, dense systems accomplish percolation in the early stage, whereas local condensation proceeds until the late stage.
% Conclusion of colloidal gelation
In both cases of gelation, percolation is a consequence of condensation frustrated by hydrodynamic interactions, whereas the coarsening process is frustrated by mechanical tensions.
%General impacts
Generally, colloidal suspensions are model cases of the binary mixtures that consist of small and big components.
Our study shed a new light on not only colloidal gelation but also dynamically asymmetric mixtures, which include polymer solutions and protein solutions.

>>>>

\section{Conclusion}
